
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% You should *also* have a ND formatting guide to ensure that you have
% all the relevant parts, put the captions in the right place, etc.
% Just because you have this wonderful style classfile doesn't mean
% that it removes *all* the formatting onus from you.  :-)
% Although be warned that the Graduate School has been known to let
% their official formatting guide get out of date. When in doubt,
% the Microsoft Word example seemed to be the only thing kept
% consistently up-to-date in 2013, and is probably the safest thing
% to consult.
%
% You should break all of this stuff up into separate files
% (at the very least, one chapter per file) and use the \include
% command, as has been done here for chapters 1 and 2 and the appendix.
% There is also an \input command, but \include is more commonly used to
% import chapters in books and dissertations. For the differences between these
% two commands, see, e.g.,
% http://web.science.mq.edu.au/~rdale/resources/writingnotes/latexstruct.html
% or http://tex.stackexchange.com/questions/246/when-should-i-use-input-vs-include.
%
% If you compile from the command line, note that you should also have
% a good Makefile; one that invokes LaTeX as many times as necessary
% (up to 4) and bibtex if necessary.
%
% If you use an editor that allows you to compile from within the
% program, note that you will need to compile up to four times. Also,
% we recommend that you use pdflatex (sometimes displayed as
% LaTeX => PDF) to compile directly to pdf.
%
% If you have any suggestions, comments, questions, please send e-mail
% to: dteditor@nd.edu
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[review,numrefs,sort&compress]{nddiss2e}
\documentclass[final,numrefs,sort&compress,noinfo]{nddiss2e}

\usepackage{ mathrsfs }
\usepackage{mathtools}
\usepackage{bbold}
\usepackage{amsmath}
%\usepackage{enumitem}
\usepackage{subfigure}
\usepackage{lineno}
\usepackage{multirow}
\usepackage{ amssymb }
\usepackage{epigraph}
\usepackage{cancel}
\setlength{\epigraphwidth}{5in}
\usepackage{caption}
\usepackage{hyperref}

\renewcommand{\textflush}{flushepinormal}
\renewcommand{\epigraphsize}

\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}

% \setlist[itemize]{leftmargin=45mm}
% One of the options draft, review, final must be chosen.
% One of the options textrefs or numrefs should be chosen
% to specify if you want numerical or ``author-date''
% style citations.
% Other available options are:
% 10pt/11pt/12pt (available with draft only)
% twoadvisors
% noinfo (should be used when you compile the final time
%         for formal submission)
% sort (sorts multiple citations in the order that they're
%       listed in the bibliography)
% compress (compresses numerical citations, e.g. [1,2,3]
%           becomes [1-3]; has no effect when used with
%           the textrefs option)
% sort&compress (sorts and compresses numerical citations;
%           is identical to sort when used with textrefs)

\begin{document}

\input{symbols.tex}

\newlength\cmsTabSkip
\setlength\cmsTabSkip{2ex}


\frontmatter % All the items before the first chapter go in ``frontmatter''

% Titles may be 1-4 lines long. If your title is longer than 4 lines,
% the class file may have difficulty formatting the title page.
% Line-breaks in the title have to be protected with `\protect`.
\title{Search for lepton flavor violating decays of \protect\\ the Higgs boson to a muon and a tau lepton \protect\\ or to an electron and a tau lepton}
\author{Prasanna Kumar Siddireddy}
\work{Dissertation} % or \work{Thesis}
\degaward{Doctor of Philosophy} % or
%\degaward{Master of Science \\ in \\ Subject}
\advisor{Colin Philip Jessop}
\department{Physics}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Front stuff
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\makepublicdomain
\copyrightholder{Prasanna Kumar Siddireddy} % If you're not the copyright holder
\copyrightyear{2020}
\makecopyright

% An abstract is optional for a mster's thesis, and required for a doctoral dissertation.
\begin{abstract}
This dissertation presents searches for lepton flavor violating decay of the standard model Higgs boson into a muon and a tau lepton or to an electron and a tau lepton. Data collected by the CMS detector in 2016-2018, in proton-proton collisions at the LHC, at a center-of-mass energy of 13\,TeV corresponding to an integrated luminosity of $137~\fb$ was used to perform the search. The observed (expected) upper limits on the branching fraction of Higgs boson decaying into a muon and a tau lepton, $\mathcal{B}(\Hmt)$, were set at 0.15 (0.15)\,\% at 95\% CL and the branching fraction of Higgs boson decaying into an electron and a tau lepton, $\mathcal{B}(\Het)$, were set at 0.22 (0.16)\,\% at 95\% CL. These are the most stringent limits set on these processes to date.

\end{abstract}

% A dedication is optional.
\renewcommand{\dedicationname}{Dedicated to}

\begin{dedication}
  To my grandfather, Venkata Rao Bandi, \\an honest and humble man. \\My grandmother, Ramanamma Bandi, \\a kind and courteous woman. \\My mother, Vijaya Lakshmi Siddireddy, \\for her love and care. \\My father, Srinivasa Rao Siddireddy, \\for his gentleness and generosity.
\end{dedication}

% These are required, and must be in this order.
\tableofcontents
\listoffigures
\listoftables

% A preface is optional.
%\begin{preface}
%  Long time ago in a galaxy far far away....(preface is optional)
%\end{preface}

% It's hard to tell from the information available from the Graduate
% School in Spring 2013 whether or not an acknowledgements section is optional.

\begin{acknowledge}

  I express my gratitude to my Ph.D. advisor and mentor, Prof. Colin Jessop. Prof. Colin has provided me with an environment where I can completely focus on my research. He has been supportive and has given positive feedback throughout my Ph.D., which helped me grow as an individual. He has addressed my concerns quickly, and I am glad to be his graduate student.

  I thank my committee members, Prof. Adam Martin, Prof. Mike Hildreth, and Prof. Umesh Garg, for taking the time to review my research and encouraging me along the process with their feedback. I would also like to thank Prof. Nancy Marinelli for helping and working with me on several projects. I am also thankful to Nikitas Loukas and Alexander Ledovskoy for their guidance on the projects I worked on with them.

  Dr. Giacomo Cuciatti has been a great mentor and friend and had made my stay at CERN enjoyable. I thank him for his guidance on the projects I worked with and accompanying me on my motorcycle diaries across Europe. Dr. Silvia Taroni was a hard-working and dedicated postdoctoral fellow. I thank her for helping me get accustomed to the software framework and guiding me to understand the details of the analysis. Dr. Nabarun Dev has been a supportive colleague and a good friend. He has helped me throughout my Ph.D., and I will always be glad to have met him.

  Dr. Maria Cepada has continuously encouraged me and provided me with all the necessary resources to finish my research. She has been a great motivator and an excellent advisor, and I thank her for taking the time to get involved in the current analysis. I thank my analysis group members: Lourdes Urda and Varun Sharma, for taking an active interest in the analysis and providing me with timely support and feedback.

  I thank the Notre Dame Physics Department for nurturing and supporting my growth as a scientist. I would especially like to thank Shari Herman in the physics office for helping me through many tasks over the years. I want to thank my friends and colleagues Saurabh Bansal, Nirupama Sensharma, Wenzhao Li, Reyer Band, Abhishek Das, Atul Kedia, Fanbo Meng, Ka Wa Ho, Lynne Lutton, Lara Zygala, Andrew Wightman, Kelci Mohrman, Nirmal Raj.

  I thank my close friends, Pratyush Pandey, Saurabh Bansal, Khalique Newaz, and Shilpi Kumar, for being there and making my stay at Notre Dame a pleasant and wonderful journey.

  Lastly, I would like to thank all the scientists, technicians and engineers, associated with CMS and LHC, whose collective work has made this thesis possible.

\end{acknowledge}

% A symbols section is optional.

% \begin{symbols}
%   \sym{c}{speed of light}
%   \sym{h}{Standard Model Higgs}
%   \sym{h125}{Standard Model Higgs}
%   \sym{H}{Heavy Higgs}
%   \sym{m}{mass}
%   \sym{e}{elementary charge}
%   \sym{E}{energy}
%   \sym{\pt}{Transverse Momentum}
%   \sym{\mcol}{Collinear Mass}
%   \sym{\mt}{Transverse Mass}
% \end{symbols}

\mainmatter
% Place the text body here.
%\include{chapter-one}
%Begin each chapter with \chapter{Title}. Both the thesis title and
%chapter titles should match in style.

%
% An unnumbered chapter (features)
%
\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}
\include{chapter6}
\include{chapter7}
\include{chapter8}
\include{chapter9}
\include{chapter10}
%
% Appendix (optional)
%
\appendix
\include{appendixA}
\include{appendixB}

%
% Back stuff
%

% % comment out the following three lines
% if using chapter-wise bibliography

\backmatter

\bibliographystyle{unsrtnat}%\bibliographystyle{abbrvnat} % The standard abbrvnat style should be acceptable. Also provided with both the advanced and standard
\bibliography{thesis}  % distributions are nddiss2e and nddiss2enoarticletitles style options.
% If you prefer to manually enter your bibliography, that is fine. Comment out the previous two lines, and enter your bibliography
% as usual. Note that if you choose this route, formatting the bibliography is your responsibility. An example is below, including the
% optional arguments necessary for author-date style citations.
%	\begin{thebibliography}{9}
%		\bibitem[Galmira(1998)]{galmira98:_gnus_milit} G.\ Galmira. Gnus and the military -- a secret conspiracy? \emph{Growing Towards Gnu}, III(7):22--183, September 1998.
%
%		\bibitem[Ganston and Greenfield(1998)]{gnus98:_gerry_ganst} G.\ Ganston and G.\ Greenfield. \emph{Gnus and You: The Art of Being New}. volume I. Grapping Books, NY, August, 1998.
%
%		\bibitem[Gloonston(1998)]{gloonston98:_gnuly_discov_gnus} G.\ Gloonston. Newly discovered gnus: The LoG. \emph{Growing Towards Gnu}, II(12):23---57, March 1998.
%
%		\bibitem[Greenfield(1996)]{greenfield96:_gettin_know_gnu} G.\ Greenfield. \emph{Getting to Know Gnu}. PhD thesis, Geoffrey Garfield School of Gnus, August 1996.
%
%		\bibitem[van Gairley(2000)]{gairley2000} G.\ van Gairley. Gnu's review. Website, 2000. \url{http://www.gairley.gnu}.
%	\end{thebibliography}

\end{document}

% End of ``example.tex''
